---
title: "MMRFBiolinks Introduction"
date: "`r BiocStyle::doc_date()`"
author:
- name: First Author
  affiliation: First Author's Affiliation
- name: Second Author
  affiliation: Second Author's Affiliation
  email: corresponding@author.com
package: MMRFBiolinksX

output: BiocStyle::html_document
vignette: >
  %\VignetteIndexEntry{"1. Introduction"}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

MMRFBiolinks is an extension of [TCGAbiolinks package](https://bioconductor.org/packages/TCGAbiolinks/)
for searching, downloading and preparing data from the Multiple Myeloma Research Foundation (MMRF) CoMMpass study available at the NCI's Genomic Data Commons (GDC) Data Portal. 



# Citation
If you use MMRFBiolinks, please cite:


<hr>
# Installation
<hr>


# Question and issues
<hr>
Please use [Github issues](https://github.com/MarzyUnicz/MMRFBiolinksX/issues) if you want to file bug reports or feature requests


# Required libraries
<hr>
The examples in this tutorial use the following libraries: 
```{r message=FALSE, warning=FALSE, include=TRUE}
library(TCGAbiolinks)
library(dplyr)
library(DT)
```

# Session info
<hr>
```{r}
version
packageVersion("MMRFBiolinksX")
```
